Probabilistic Catalogs for Crowded Stellar Fields

### 2012-11-20 paper/ms.tex
Writing conclusions

\section{Discussion and Conclusions}\label{sec:conclusion}

@@

What have we achieved?

What are the limitations of what we have done?  Limitations include
PSF knowledge (and simplicity), simple number--flux relationship, no
astrophysical model.  On the latter, I mean: No model of temperatures,
masses, distances, reddening and so on.  We also haven't thought about
multi-epoch, multi-band imaging, where you have to consider the
motions and variations and spectral energy distributions of stars.  On
this latter point, we should cite Lang et al (faint motion).  Each of
these limitations should get its own paragraph, really.

What kinds of new science will this enable?  One example would be IMF
inference in dense stellar clusters.  Another could be modeling of
distant galaxies in terms of their stellar components.  Most
importantly, astrophysics can proceed without taking the hard,
information-lossy step of fixing a catalog, somewhere between the raw
data and the science of interest!

>>>>

\section{Discussion and Conclusions}\label{sec:conclusion}
%What have we achieved?

In this paper we have developed and demonstrated a fully Bayesian approach to
making catalogs from astronomical images in the case where the image contains
only stars (or other point sources).

@@

In practice, it may also be necessary to improve the model for the prior
distribution
of stellar positions and fluxes. One area where this is clearly needed is the
application of this approach to images of stellar clusters. The model would need
to be revised to take into account the fact that we expect the stars' positions
to be clustered together, whereas the current model implies a large prior
probability for the stars being scattered evenly across the image. In this and
other applications, the luminosity function would also require multiple
components, for example consisting of stars that are associated with a cluster
or a stream and those that are not.

Throughout this paper, we have also assumed that the pixel-convolved PSF can
be adequately modeled using simple components and that there are no PSF
variations across the field. Relaxing this assumption provides a significant
challenge for the future.

{\bf Needs more words}

%What are the limitations of what we have done?  Limitations include
%PSF knowledge (and simplicity), simple number--flux relationship, no
%astrophysical model.  On the latter, I mean: No model of temperatures,
%masses, distances, reddening and so on.  We also haven't thought about
%multi-epoch, multi-band imaging, where you have to consider the
%motions and variations and spectral energy distributions of stars.  On
%this latter point, we should cite Lang et al (faint motion).  Each of
%these limitations should get its own paragraph, really.

%What kinds of new science will this enable?  One example would be IMF
%inference in dense stellar clusters.  Another could be modeling of
%distant galaxies in terms of their stellar components.  Most
%importantly, astrophysics can proceed without taking the hard,
%information-lossy step of fixing a catalog, somewhere between the raw
%data and the science of interest!
